Consistent Polyhedral Surrogates via Embedding

### 2019-05-21 notes/jessie-proof-sketches.tex
My brain hurts.  I'll revisit in the morning

  To start, assume that $\risk{L} = \risk{\ell}$.
  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
  As $\ell$ is discrete, we know $\gamma$ is finite \raf{note for later: we have to be careful about ``discrete'' and ``finite'' since they both bake in regularity conditions, like nondegeneracy as you mention, but also non-redundancy}, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$ if $\ell(r) = L(\varphi(r))$ for all $r \in \R$.

  To see this, assume that for some $r \in \R$ that $\ell(r) \neq L(\varphi(r))$.
  Then for any distribution $p$ such that $p \in \gamma_r$, we know that $r \in \argmin_{r'} \ell(r', p)$.
  If $\ell(r, p) < L(\varphi(r), p)$, then we contradict the embedding result of the properties, as $r \in \gamma(p)$, but $\varphi(r) \not\in \Gamma(p)$, as there is some other report that yields a strictly lower loss for $L$.
  Similarly, for any $p' \in \Gamma_{\varphi(r)}$, we know that $\varphi(r) \in \argmin_u L(u, p')$.
  If $\ell(r, p') > L(\varphi(r), p')$, then we again contradict the property embedding, as $\varphi(r) \in \Gamma(p')$, but $r \not\in \gamma(p')$.
  However, there is some other report that yields a lower loss for $\ell$, given that the risks are the same.
  Therefore, we must have $\ell(r) = L(\varphi(r))$ for all $r \in \R$, and conclude that $L$ embeds the discrete loss $\ell$.

>>>>

  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know these risks are polyhedral, as $\risk{\ell}$ is the pointwise min of a finite set of linear functions.
  The projection of their epigraphs onto $\simplex$ must form the same power diagram \jessie{COLT Theorem 33}.  %, corresponding to the level sets of the properties each loss elicits.
  Observe there are only finitely many cells in a power diagram; we call the set of full-dimensional cells in the power diagram $F$.
  We claim that each cell $f \in F$ is then a level set $\gamma_r$ for some $r \in \R$, and equivalently, $\Gamma_{u_f}$ for some $u_f \in \reals^d$.
  We go on to embed $\varphi: r \mapsto u_f$ for each $r \in \R$.

  Now, for each $f \in F$, fix some distribution $p \in \inter{f}$.
  The supporting hyperplane of $\risk{\ell}(p)$ is unique, since $p$ belongs to exactly one facet of $\risk{\ell}$ (i.e. $\risk{\ell}(p)$ is differentiable.)
  Since $\ell$ is discrete, the coefficients of the supporting hyperplane exactly describe the loss over each outcome given the report $r = \gamma(p)$.  \jessie{??}
  %Similarly, for some $u \in \reals^d$, as the risks are the same, we claim that $L(u,p) = \ell(\gamma(p), p)$, as the risks are equal.

  As there is some $u_f \in \argmin_{u'} L(u', p)$, we can design $\varphi : r \mapsto u_f \in \Gamma(p)$, and by the risks being equal, we also have $r \in \argmin_{r' \in \R} \ell(r', p)$, and thus $r \in \gamma(p)$.
  The reverse implication follows similarly, and we conclude that $\Gamma$ embeds $\gamma$.

  Since $\risk{L}$ is polyhedral, the supporting hyperplane to $\risk{L}$ is unique for each $p \in \inter{f}$ and $f \in F$, and so is the loss $L(u_f)$ is unique for all such $p$.
  As both the loss values of $\ell(r)$ and $L(u_f)$ are equal and minimize their respective losses,  so we conclude that $L$ embeds $\ell$.

%  To start, assume that $\risk{L} = \risk{\ell}$.
%  The projection of the epigraphs onto $\simplex$ must then form the same power diagram \jessie{COLT Theorem 33}, corresponding to the level sets of the properties each loss elicits.
%  Notably, \jessie{as in proof of COLT Prop 12,} the facets of $\risk{\ell}$ project onto the level sets of $\gamma := \prop{\ell}$.
%  As $\ell$ is discrete, we know $\gamma$ is finite \raf{note for later: we have to be careful about ``discrete'' and ``finite'' since they both bake in regularity conditions, like nondegeneracy as you mention, but also non-redundancy}, and so the level sets of $\gamma$ are full-dimensional \jessie{by COLT Lemma 10} and union to the simplex by nondegeneracy of $\gamma$.
%  Since the risks of $L$ and $\ell$ are the same (and therefore, so are their projections onto $\simplex$), this same [finite] subset $\Theta$ of the level sets of $\Gamma$ that union to the simplex and are full-dimensional.
%  By \jessie{COLT Prop 12}, we can then conclude that $\Gamma$ embeds the finite property $\gamma$, \raf{wait, you skipped the other condition for losses embedding each other $\rightarrow$} and thus $L$ embeds the discrete loss $\ell$ if $\ell(r) = L(\varphi(r))$ for all $r \in \R$.
%  
%  To see this, assume that for some $r \in \R$ that $\ell(r) \neq L(\varphi(r))$.
%  Then for any distribution $p$ such that $p \in \gamma_r$, we know that $r \in \argmin_{r'} \ell(r', p)$.
%  If $\ell(r, p) < L(\varphi(r), p)$, then we contradict the embedding result of the properties, as $r \in \gamma(p)$, but $\varphi(r) \not\in \Gamma(p)$, as there is some other report that yields a strictly lower loss for $L$.
%  Similarly, for any $p' \in \Gamma_{\varphi(r)}$, we know that $\varphi(r) \in \argmin_u L(u, p')$.
%  If $\ell(r, p') > L(\varphi(r), p')$, then we again contradict the property embedding, as $\varphi(r) \in \Gamma(p')$, but $r \not\in \gamma(p')$.
%  However, there is some other report that yields a lower loss for $\ell$, given that the risks are the same.
%  Therefore, we must have $\ell(r) = L(\varphi(r))$ for all $r \in \R$, and conclude that $L$ embeds the discrete loss $\ell$.
